Issue area

### 2023-09-14 notebook/analysis-issue.qmd
Show ci in plot instead of median

```{r plot-pred-discrete-continuous-local, message=FALSE, fig.width=6, fig.height=6}
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

ggplot(preds_issue_plot, aes(x = issue_area_nice, y = prop)) +
  stat_pointinterval(color = clrs[5], fatten_point = 1) +
  expand_limits(y = 0) +
  facet_wrap(vars(outcome), ncol = 1) +
  scale_x_discrete(labels = label_wrap(10)) +
  scale_y_continuous(labels = label_percent()) +
  labs(x = NULL, y = "Proportion of predictions") +
  theme_ongo()
```

>>>>

```{r plot-pred-discrete-continuous-local-bars, fig.width=8, fig.height=3, out.width="100%"}
preds_issue_plot <- preds_issue |> 
  left_join(issue_indicator_lookup, by = join_by(issue_area)) |> 
  mutate(outcome = case_when(
    .prediction == 0 ~ "1 province",
    .prediction > 0 & .prediction < 1 ~ "1–32 provinces",
    .prediction == 1 ~ "32 provinces"
  )) |> 
  group_by(outcome, issue_area_nice, draw) |> 
  summarize(count = n()) |> 
  group_by(issue_area_nice, draw) |> 
  mutate(prop = count / sum(count))

preds_issue_plot_order <- preds_issue_plot |> 
  filter(outcome == "32 provinces") |>
  group_by(issue_area_nice) |> 
  summarize(median_prop = median(prop)) |> 
  arrange(median_prop) |> 
  mutate(issue_area_nice_labels = str_wrap(issue_area_nice, 15)) |> 
  mutate(issue_area_nice = fct_inorder(issue_area_nice))

preds_issue_text <- preds_issue_plot |> 
  group_by(outcome, issue_area_nice) |> 
  summarize(median_prop = median_qi(prop)) |> 
  unnest(median_prop) |> 
  group_by(issue_area_nice) |> 
  mutate(y_plot = (y / 2) + lag(cumsum(y), default = 0)) |> 
  mutate(y_plot = 1 - y_plot) |> 
  mutate(prop_nice = label_percent(accuracy = 1)(y)) |>
  mutate(prop_ci_nice = glue::glue(
    "{ymin}–{ymax}",
    ymin = label_number(accuracy = 1, scale = 100)(ymin),
    ymax = label_percent(accuracy = 1)(ymax)
  )) |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  ))

preds_issue_plot |> 
  mutate(issue_area_nice = factor(
    issue_area_nice, 
    levels = preds_issue_plot_order$issue_area_nice,
    labels = preds_issue_plot_order$issue_area_nice_labels
  )) |> 
  ggplot(aes(x = draw, y = prop)) +
  geom_col(aes(fill = outcome), position = "stack", linewidth = 0, width = 1) +
  geom_text(
    data = preds_issue_text,
    aes(x = 250, y = y_plot, label = prop_ci_nice),
    size = 3, fontface = "bold", color = "white"
  ) +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(labels = label_percent(), expand = c(0, 0)) +
  scale_fill_manual(values = clrs[c(3, 5, 7)]) +
  facet_wrap(vars(issue_area_nice), strip.position = "bottom", nrow = 1) +
  labs(x = NULL, y = "Proportion of predictions", fill = NULL) +
  theme_ongo() +
  theme(
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.spacing = unit(5, "pt"),
    strip.text = element_text(vjust = 1, hjust = 0.5, size = rel(0.8), face = "plain")
  )
```
